---
title: "Getting started with gcalendr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with gcalendr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE}
library(gcalendr)
```

## Quickstart ##

This is a short document on getting up to speed with `gcalendr` quickly.

## External Setup ##

In order to use `gcalendr` you will need to create a google project for it. The
easiest way to do this is via the 
[Python Quickstart](https://developers.google.com/gmail/api/quickstart/python).

* Click the `Enable the Gmail API` button.

* In the resulting dialog click the `DOWNLOAD CLIENT CONFIGURATION` on your computer.

* Tell `gcalendr` where the JSON lives, by doing one of the two things

    1. Call `calendar_auth_configure(path = "path/to/downloaded/json")`
  
    2. Set the `gcalendr_APP` environment variable to the location of the JSON
file, it is convenient to do this in your `.Renviron` file with
`usethis::edit_r_environ()`. Then calling `calendar_auth_configure()` with no arguments.

* Call `calendar_auth()` to start the OAuth flow to verify to google that you would
like your `gcalendr` project to have access to your email. You will get a scary
warning about an untrusted application, this is because the application is
the one you just created, click advanced and `Go to gcalendr` to proceed to do
the oauth flow.

* If you want to authenticate with fewer scopes than the default use the
`scopes` parameter to `calendar_auth()`. You can see a full list of available
scopes from `calendar_scopes()`.

Only very heavy usage of the Gmail API requires payment, so use of the API for most
people should be free.

If you use `usethis::edit_r_environ()` to set both `gcalendr_EMAIL` and
`gcalendr_APP`, then once you have an oauth token you can simply run
`calendar_auth_configure()` with no arguments at the top of the script to setup your
application.


## Example ##

```{r eval=FALSE}
library(gcalendr)

## Set up google oauth permissions
## This will prompt you to specify an account
calendar_auth()

```


```{r eval=FALSE}
## To specify a specific account, provide your account id, typically an email address
calendar_auth("apdevries@gmail.com")

## Retrieve tibble of available calenders
calendar_ids <- calendar_list()
calendar_ids

## Retrieve tibble of events from a specific calendar

my_cal_id <- "apdevries@gmail.com"
events <- calendar_events(my_cal_id, days_in_past = 90, days_in_future = 90)
events
```
